Drought regimens predict life history strategies in \emph{Heliophila}

### 2019-08-19 manuscript/manuscript.Rmd
minor spelling
moved example VHI datasets to data folder

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word

@@

drought<-raster::raster("~/VHI/raster/VHP.G16.C07.npp.P2015050.VH.nc.grd")
drought <-crop(drought, rbind(c(12,37),c(-35, -18)))

@@

nondrought<-raster::raster("~/VHI/raster/VHP.G16.C07.NJ.P1999050.VH.hdf.h5.grd")
nondrought <-crop(nondrought, rbind(c(12,37),c(-35, -18)))

@@

typical<-raster::raster("~/VHI/raster/VHP.G16.C07.NP.P2012050.VH.hdf.h5.grd")
typical <-crop(typical, rbind(c(12,37),c(-35, -18)))

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

@@

drought<-raster::raster("../data/VHP.G16.C07.npp.P2015050.VH.nc.grd")
drought <-crop(drought, rbind(c(12,37),c(-35, -18)))

@@

nondrought<-raster::raster("../data/VHP.G16.C07.NJ.P1999050.VH.hdf.h5.grd")
nondrought <-crop(nondrought, rbind(c(12,37),c(-35, -18)))

@@

typical<-raster::raster("../data/VHP.G16.C07.NP.P2012050.VH.hdf.h5.grd")
typical <-crop(typical, rbind(c(12,37),c(-35, -18)))
